\LARGE \bf A Formal Description of Bitcoin's Script Language

### 2017-03-23 paper.tex

\subsection{Application of Script Grammar}

[Describe how grammar was used]

@@

$\bullet$ It was our hope that we could define operational semantics for op codes of previous versions of Script that caused crashes or other issues in the past.  Using these definitions, we would then show that the old definitions could be used to cause problems.  Unfortunately, there is very little documentation regarding how these errors came about.  The reference documentation itself only documents changes back to 2014 while most of the serious problems with Script were fixed in 2010. The only fix we were able to analyze was the change to \texttt{OP\_RETURN}.

@@

In this section, we make use of our formal specification to reason about execution time bounds of Script programs and to explain how a flaw in a prior version of the language was fixed.

>>>>

@@

$\bullet$ It was our hope that we could define operational semantics for op codes of previous versions of Script that caused crashes or other issues in the past.  Using these definitions, we would then show that the old definitions could be used to cause problems.  Unfortunately, there is very little documentation regarding how these errors came about.  The reference documentation itself only documents changes back to 2014 while most of the serious problems with Script were fixed in 2010. Furthermore, whenever a weakness was discovered by the Bitcoin developers themselves, they did not tell everyone exactly how to exploit the language. Thus it is known that there was a vulnerability involving the \texttt{OP\_LEFT} command, and that it was disabled as a result, but to our knowledge there is no information online about what the problem was exactly. The only fix we were able to analyze was the change to \texttt{OP\_RETURN}.

@@

In this section, we make use of our formal description to reason about execution time bounds of Script programs and to explain how a flaw in a prior version of the language was fixed.
